Verifying Demonstrations

### 2018-05-25 paper/conclusions.tex

>>>>

Finally, Mallory represents another nation state and has some interest in 
affecting the stability of Grace's regime, for Mallory's own gain, thus 
supporting either Grace or Alice as she see fits.
Thus, the objective of Mallory will also be to either increase or decrease the count.
\seb{we have to justify why Mallory is not captured either by Alice or Grace}
\daniel{I think that we can move Mallory to the discussion, because Mallory 
  cannot get valid credentials for herself as a foreign state.}
In addition, Mallory could also have simply as her objective to cause a 
denial-of-service attack on the architecture of \PRIVO.

She cannot create keys valid in another nation state.
